Hybrid platforms and bargaining power

### 2024-07-21 src/paper/application.tex
Mention that proofs are through more general results in the appendix

I will now present the main results of the model, again, starting from the final subgame and working backwards.
For each subgame, I also demonstrate that the equilibrium exists and is unique, and therefore the complete game also has a unique equilibrium.
The propositions in this section are generally proven for a more general framework, and those presented here are special cases of those.
For this reason, the proofs are also presented together with the more general model in \Cref{sec:more_general}.

>>>>

I will now present the main results of the model, again, starting from the final subgame and working backwards.
For each subgame, I also demonstrate that the equilibrium exists and is unique, and therefore the complete game also has a unique equilibrium.
The propositions in this section are generally proven for a more general framework, and those presented here are special cases of those.
The reason for presenting the more special case in the main text is twofold.
First, it the more concrete model is better for expositional purposes, and is a good fit for the setting.
Second, the link between consumer surplus and the number of products is straightforward under the logit assumption, making it possible to state welfare results, as well.

For this reason, the proofs are also presented together with the more general model in \Cref{sec:more_general}.
Most of the results only rely on \Cref{ass:additive_profit,ass:free_entry,ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:single_crossing}, and do not require the specific, logit-like demand function described previously.
Therefore, I proceed to prove those results in two steps.
First, I demonstrate that the model satisfied the aforementioned assumptions.
Second, in \Cref{sec:more_general}, I prove the corresponding results for the more general case.
